### 2023-05-01 conference-paper/main.tex
Fixed some formating and scentence issues

\section{Introduction}
% Message 1: Motivation to incorporate low-emission fuels and techniques
The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high bypass ratio (UHBR) engines with small cores and high overall pressure ratios (OPR).
Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits.
However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
We introduce a closed-loop water recirculation model that demonstrates the possible efficiency gain when hydrogen is used for purposes other than combustion.
% In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHBR ratio turbofan engines.
% We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
% [x] TODO: PA-PA, add section about MAUD and cite.

@@

% [x] TODO: AL-PA, Remove the black box with the component descriptions from the bottom left of the figure.
% [x] TODO: AL-PA, Add the description of the figure elements to the caption.
% [x] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
% [x] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1.0\textwidth]{N3_cycle.pdf}
    \caption{
        Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}.
        Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
    }
    \label{fig:N3_original}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
    \caption{
        The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
        The water vapor recovery system (extractor) extracts a fraction of the water in the core stream and reinjects it upstream of the high-pressure compressor.
        This diagram illustrates the feedback effect that this implementation has on the overall core flow.}
    \label{fig:n3_cycle}
\end{figure}

To account for the humidity of the inlet air as well as the increased humidity after water injection, we modified the composition of the air mixture upstream of the combustor.
% Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
% To utilize water engine section infront of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
pyCycle provides a \texttt{wet-air} dataset that introduces $\mathrm{H_2O}$ molecules to the composition of air.
% The \texttt{wet-air} dataset inherits the NPSS \texttt{JANAF} data from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
% The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of $\mathrm{H_2O}$ to air in the reactants of the inflow mixture.
% In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
% The WAR is the sp of the air expressed in equal units and separating out the total mass (kg water/kg air).
\citet{Kalnay1996} give the humidity values for each flight condition.
% The humidity values used in this paper are from a NOAA dataset \cite{Kalnay1996}.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1.0\textwidth]{N3_CLVR_cycle.pdf}
    \caption{
        Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
        Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
    }
    \label{fig:n3_clvr}
\end{figure}

@@

Therefore, TSEC at the cruise condition is the objective function in the optimzation problem.
An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_opt_xdsm}.

@@

The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
Only the water recovery fraction at CRZ is a design variable since we are optimizing $TSEC_{\rm{CRZ}}$.
TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation \eqref{t4ratio}.
\begin{equation}
    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
    \label{t4ratio}
\end{equation}

@@

The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.

% [x] TODO: AL - PA, Define the T4 ratio with an equation and reference the equation in the table
% [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
% [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
% [ ] TODO: PA-PA, explain variable ranges
\begin{table}[hbt!]
    \centering
    \caption{
        Multipoint optimization problem definition.
        The objective function is the thrust specific energy consumption at the cruise condition.
        The constraints are net thrust and engine diameter constraint at the design point, TOC.
    }
    \small
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{r l l r l}
        \toprule
                        & Variable/Function              & Description                                                           & Units          & Quantity \\
        \hline
        minimize        & $\rm{TSEC}_{\rm{CRZ}} $        & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/s}     & 1        \\
                        &                                &                                                                       &                &          \\
        with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery fraction at CRZ                                        & -              & 1        \\
                        & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                & -              & 1        \\
                        & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                            & -              & 1        \\
                        & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                            & -              & 1        \\
                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                             & \si{\degree R} & 1        \\
                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation \eqref{t4ratio})               & -              & 1        \\
                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation \eqref{vratio}) & -              & 1        \\
        \cline{3-5}
                        &                                & Total                                                                 &                & 7        \\
                        &                                &                                                                       &                &          \\
        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                              & \si{lbf}       & 1        \\
                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                  & \si{inch^2}    & 1        \\
        \cline{3-5}
                        &                                & Total                                                                 &                & 2        \\
        \bottomrule
    \end{tabular}
    \label{tab:opt_problem}
\end{table}

\begin{table}[hbt!]
    \centering
    \caption{Design variable ranges for the optimization problem.
    }
    \small
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{l l l l}
        Design Variable       & Lower  & Upper  & Units     \\
        \toprule
        $x_{H2O,CRZ}$         & 0.0    & -      & -         \\
        $PR_{fan,TOC}$        & 1.2    & 1.4    & -         \\
        $PR_{LPC,TOC}$        & 2.5    & 4.0    & -         \\
        $PR_{OPR,TOC}$        & 40.0   & 70.0   & -         \\
        $T_{4,TOC}/T_{4,RTO}$ & 0.5    & 0.95   & -         \\
        $T_{4,RTO}$           & 3000.0 & 3600.0 & $^\circ$R \\
        $V_{ratio,CRZ}$       & 1.35   & 1.45   &           \\
        \bottomrule
    \end{tabular}
    \label{tab:res_full_opt_H2}
\end{table}

@@

Our fuel performance metric is TSEC but minimizing $\dot{m}_{fuel}$ is a better posed optimization problem since we will also have thrust constraints.
Therefore, the fuel flow rate at CRZ, $\dot{m}_{fuel,CRZ}$, was set as the objective.

@@

The recirculation system is implemented by introducing two new custom pyCycle components, the water extractor and injector, which form a continuous closed-loop feedback water flow in the engine.
We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
System-level \emph{balance} constraints on the engine are described to show how a reduced-space optimization problem can be developed.
The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, presusres and velocities within the engine.
An additional design variable controlling how much water is recirulated is added at the CRZ point to improve the fuel burn.

@@

\section{Acknowledgements}

>>>>

\section{Introduction}
% Message 1: Motivation to incorporate low-emission fuels and techniques
The effects of climate change are pushing the aviation industry towards hydrogen-fueled propulsion systems as a solution to reduce emissions.
N+3 technology estimates for turbofan engines that burn hydrocarbon fuels suggest that higher efficiency can be achieved by designing ultra high bypass ratio (UHBR) engines with small cores and high overall pressure ratios (OPR).
Higher OPR and smaller cores challenge the limits of compressor and turbine design, placing an upper bound on potential performance and emissions improvements.
Switching to hydrogen as the primary fuel source reduces carbon dioxide emissions immediately, but adds complexity and weight that offset the benefits%~\cite{Adler2023}.
However, hydrogen is a versatile fuel with advantageous chemical and thermodynamic properties that can be exploited to increase the performance and reduce emissions.
We introduce a closed-loop water recirculation model that demonstrates the possible efficiency gain when hydrogen is used for purposes other than combustion.
% In this study, we investigate the tradeoff between burning hydrocarbon fuels like Jet-A versus hydrogen for UHBR ratio turbofan engines.
% We will look at new ideas with water recirculation to further squeeze performance and efficiency from Jet-A and hydrogen combustion using gradient-based design optimization.
% [x] TODO: PA-PA, add section about MAUD and cite.

@@

% [x] TODO: AL-PA, Remove the black box with the component descriptions from the bottom left of the figure.
% [x] TODO: AL-PA, Add the description of the figure elements to the caption.
% [x] TODO: AL-PA, Consider changing the caption to "Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}"
% [x] TODO: AL-PA, Remove the flight conditions component and add the bypass duct component below the splitter. I think the bypass is an important enough aspect of the engine to include.
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1.0\textwidth]{N3_cycle.pdf}
    \caption{
        Simplified layout of the N+3 engine cycle, adapted from~\citet{Hendricks2019}.
        Black arrows are flow connections, red lines are mechanical connections, blue boxes are cycle elements, red boxes are shaft elements.
        Flow stations are identified with bubble text
    }
    \label{fig:N3_original}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.75\textwidth]{turbofan_wvr.pdf}
    \caption{
        The configuration of a high-bypass turbofan model with an integrated closed-loop water vapor recovery and injection system.
        The water vapor recovery system (extractor) extracts a fraction of the water in the core stream and re-injects it upstream of the high-pressure compressor.
        This diagram illustrates the feedback effect that this implementation has on the overall core flow.}
    \label{fig:n3_cycle}
\end{figure}

To account for the humidity of the inlet air as well as the increased humidity after water injection, we modified the composition of the air mixture upstream of the combustor.
% Since water is being used in the sections of the engine upstream of the combustor, this model was designed to take the humidity of the air into account.
% To utilize water engine section in front of the combustor the N+3 engine model had to be modified to include $H_2O$ as a species.
pyCycle provides a \texttt{wet-air} dataset that introduces $\mathrm{H_2O}$ molecules to the composition of air.
% The \texttt{wet-air} dataset inherits the NPSS \texttt{JANAF} data from the original model but removes a couple troublesome hydrocarbons from the product species as they can cause numerical issues.
% The FlightConditions() pyCycle subsystem can then have a reactant and mixture ratio specified when implemented.
We prescribe atmospheric mass-specific humidity as a water-to-air ratio (WAR) that is defined as the ratio of $\mathrm{H_2O}$ to air in the reactants of the inflow mixture.
% In this case, the reactant is be $H_2O$ and the mixture ratio is the water-to-air (WAR) ratio of the water content in the air.
% The WAR is the sp of the air expressed in equal units and separating out the total mass (kg water/kg air).
\citet{Kalnay1996} give the humidity values for each flight condition.
% The humidity values used in this paper are from a NOAA dataset \cite{Kalnay1996}.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1.0\textwidth]{N3_CLVR_cycle.pdf}
    \caption{
        Simplified layout of the N+3 engine cycle with the closed-loop vapor recovery.
        Black arrows are flow connections, blue boxes are cycle elements
        Flow stations are identified with bubble text.
    }
    \label{fig:n3_clvr}
\end{figure}

@@

For this work we are concerned with minimizing fuel burn of the engine subject to known thrust constraints.
Therefore, we will use TSEC at the cruise condition to compare the two fuels but will use $\dot{m}_{\rm{fuel,CRZ}}$ as the objective function in the optimzation problem.
An XDSM diagram of the optimization problem with the multipoint formulation is shown in Figure \ref{fig:N3_opt_xdsm}.

@@

The design variables for this problem are water recovery fraction at CRZ ($X_{\rm{H_2O,CRZ}}$), fan pressure ratio ($\rm{PR}_{\rm{fan,TOC}}$), low pressure compressor pressure ratio ($\rm{PR}_{\rm{LPC,TOC}}$), overall pressure ratio at CRZ ($\rm{OPR}_{\rm{TOC}}$), burner temperature at RTO ($T_{4,\rm{RTO}}$), TOC-RTO burner temperature ratio ($T_{4,\rm{ratio}}$), and the nozzle velocity ratio at CRZ ($V_{\rm{ratio,CRZ}}$).
Only the water recovery fraction at CRZ is a design variable since we are optimizing $\dot{m}_{\rm{fuel,CRZ}} $.
TOC-to-RTO burner temperature ratio ($T_{4,\rm{ratio}}$) is shown in Equation \eqref{t4ratio}.
\begin{equation}
    T_{4,\rm{ratio}} = \frac{T_{4,\rm{TOC}}}{T_{4,\rm{RTO}}}
    \label{t4ratio}
\end{equation}

@@

The optimization problem objective function, design variables, and constraints are shown in Table \ref{tab:opt_problem} below.
The thermodynamic cycle design variable ranges are determined from the expected N+3 technology limits~\cite{Hendricks2019}.
Additionally, the design variable ranges are shown in Table \ref{tab:dv_table}.

% [x] TODO: AL-PA, Define the T4 ratio with an equation and reference the equation in the table
% [x] TODO: AL-PA, I thought we were only doing recovery fractions at CRZ??
% [x] TODO: AL-PA, Make sure you reference the equations for the DVs/cons in the descriptions so the reader can connect them.
% [x] TODO: PA-PA, explain variable ranges
\begin{table}[hbt!]
    \centering
    \caption{
        Multipoint optimization problem definition.
        The objective function is the thrust specific energy consumption at the cruise condition.
        The constraints are net thrust and engine diameter constraint at the design point, TOC.
    }
    \small
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{r l l r l}
        \toprule
                        & Variable/Function              & Description                                                           & Units           & Quantity \\
        \hline
        minimize        & $\dot{m}_{\rm{fuel,CRZ}} $     & Thrust-specific energy consumption at CRZ (Equation \eqref{eq:tsec})  & \si{lbm/hr/lbf} & 1        \\
                        &                                &                                                                       &                 &          \\
        with respect to & $X_{\rm{H_2O,CRZ}}$            & Water recovery fraction at CRZ                                        & -               & 1        \\
                        & $\rm{PR}_{\rm{fan,TOC}}$       & TOC fan pressure ratio                                                & -               & 1        \\
                        & $\rm{PR}_{\rm{LPC,TOC}}$       & TOC low-pressure compressor pressure ratio                            & -               & 1        \\
                        & $\rm{OPR}_{\rm{TOC}}$          & TOC overall pressure ratio                                            & -               & 1        \\
                        & $T_{4,\rm{RTO}}$               & RTO combustor temperature                                             & \si{\degree R}  & 1        \\
                        & $T_{4,\rm{ratio}}$             & TOC-to-RTO temperature ratio (Equation \eqref{t4ratio})               & -               & 1        \\
                        & $V_{\rm{ratio,CRZ}}$           & Core-to-bypass nozzle velocity ratio at CRZ (Equation \eqref{vratio}) & -               & 1        \\
        \cline{3-5}
                        &                                & Total                                                                 &                 & 7        \\
                        &                                &                                                                       &                 &          \\
        subject to      & $F_{\rm{net,TOC}} \geq 5800.0$ & Target net thrust at TOC                                              & \si{lbf}        & 1        \\
                        & $D_{\rm{fan}} \leq 100$        & Maximum Fan Diameter                                                  & \si{inch^2}     & 1        \\
        \cline{3-5}
                        &                                & Total                                                                 &                 & 2        \\
        \bottomrule
    \end{tabular}
    \label{tab:opt_problem}
\end{table}

\begin{table}[hbt!]
    \centering
    \caption{Design variable ranges for the optimization problem.
    }
    \small
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{l l l l}
        Design Variable          & Lower  & Upper  & Units     \\
        \toprule
        $X_{\rm{H_2O,CRZ}}$      & 0.0    & 1.0    & -         \\
        $\rm{PR}_{\rm{fan,TOC}}$ & 1.2    & 1.4    & -         \\
        $\rm{PR}_{\rm{LPC,TOC}}$ & 2.5    & 4.0    & -         \\
        $\rm{OPR}_{\rm{TOC}}$    & 40.0   & 70.0   & -         \\
        $T_{4,\rm{ratio}}$       & 0.5    & 0.95   & -         \\
        $T_{4,RTO}$              & 3000.0 & 3600.0 & $^\circ$R \\
        $V_{ratio,CRZ}$          & 1.35   & 1.45   & -         \\
        \bottomrule
    \end{tabular}
    \label{tab:dv_table}
\end{table}

@@

Our fuel performance metric is TSEC but minimizing $\dot{m}_{\rm{fuel}}$ is a more relavent problem since we will have known thrust constraints and want to compare fuel economy.
Therefore, the fuel flow rate at CRZ, $\dot{m}_{\rm{fuel,CRZ}}$, was set as the objective function.

@@

The recirculation system is implemented by introducing two new custom pyCycle components, the water extractor and injector, which form a continuous closed-loop feedback water flow in the engine.
We then described the multipoint design problem and how it is used to design an aircraft engine to meet the operating requirements at different flight regimes.
System-level \emph{balance} constraints on the engine are described to show how a reduced-space optimization problem can be developed.
The optimization problem is then introduced with constraints on the design point thrust and overall engine size with thermodynamic design variables describing the temperatures, pressures, and velocities within the engine.
An additional design variable controlling how much water is recirulated is added at the CRZ point to improve the fuel burn.
The optimization problem is then solved for four cases: with Jet-A or hydrogen fuel and with and without water recirculation.

@@

\section{Acknowledgements}
We would like to thank Justin Grey for his help with the pyCycle components of this work.
Since there is very little pyCycle documentation, his expertise and knowledge of the tool helped make the development of the custom pyCycle components possible.

### 2023-05-01 figures/N3_CLVR_cycle.tex
Fixed some formating and scentence issues

\tikzstyle{element} = [rectangle, draw, fill=elementcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{shaft_element} = [rectangle, draw, fill=shaftcolor!20,
text width=10em, text centered, font=\LARGE, rounded corners, minimum height=4em]
\tikzstyle{heat_element} = [rectangle, draw, fill=heatcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{connection} = [draw, -latex', ultra thick]
\tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
\tikzstyle{heat_flow} = [draw, -latex', ultra thick, color=heatcolor]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    % \node [element] (inlet) {Inlet};
    % \node [element, right=4em of inlet] (fan) {Fan};
    % \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (injector) {Water Injector};
    \node [element, right=4em of injector ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (extractor) {Water Extractor};
    \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
    \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
    % \node [element, below=12em of burner] (bypduct) {Bypass Duct};
    % \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};

@@

@@

>>>>

\tikzstyle{element} = [rectangle, draw, fill=elementcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{shaft_element} = [rectangle, draw, fill=shaftcolor!20,
text width=10em, text centered, font=\LARGE, rounded corners, minimum height=4em]
\tikzstyle{heat_element} = [rectangle, draw, fill=heatcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{connection} = [draw, -latex', ultra thick]
\tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
\tikzstyle{station_label} = [circle, draw, text width=2em, text centered, font=\LARGE]
\tikzstyle{connection} = [draw, -latex', ultra thick]
\tikzstyle{line} = [draw]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    % \node [element] (inlet) {Inlet};
    % \node [element, right=4em of inlet] (fan) {Fan};
    % \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (injector) {Water Injector};
    \node [element, right=4em of injector ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (extractor) {Water Extractor};
    \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
    \node [element, below=8em of burner] (vrl) {Vapor Recovery Loop};
    % \node [element, below=12em of burner] (bypduct) {Bypass Duct};
    % \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};

@@

    % Create station labels
    % \node [station_label, below=8em of inlet.west] (1) {1};
    % \node [station_label, below=6em of fan.west] (1) {1};
    % \node [station_label, below=8em of splitter.west] (13) {13};
    \node [station_label, below=6em of lpc.west] (2) {2};
    \node [station_label, below=6em of hpc.west] (25) {25};
    \node [station_label, below=6em of burner.west] (3) {3};
    \node [station_label, below=6em of hpt.west] (4) {4};
    \node [station_label, below=6em of lpt.west] (45) {45};
    \node [station_label, below=6em of corenozzle.west] (5) {5};
    % \node [station_label, below=6em of bypnozzle.west] (17) {17};

@@

    % Draw station label connections
    % \path [line] (inlet.west) -- (1.north);
    % \path [line] (fan.west) -- (1.north);
    % \path [line] (splitter.west) -- (13.north);
    \path [line] (lpc.west) -- (2.north);
    \path [line] (hpc.west) -- (25.north);
    \path [line] (burner.west) -- (3.north);
    \path [line] (hpt.west) -- (4.north);
    \path [line] (lpt.west) -- (45.north);
    \path [line] (corenozzle.west) -- (5.north);
    % \path [line] (bypnozzle.west) -- (17.north);

### 2023-05-01 figures/N3_cycle.tex
Peter's fixes 4/28
Fixed some formating and scentence issues

\tikzstyle{element} = [rectangle, draw, fill=elementcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{shaft_element} = [rectangle, draw, fill=shaftcolor!20,
text width=10em, text centered, font=\LARGE, rounded corners, minimum height=4em]
\tikzstyle{heat_element} = [rectangle, draw, fill=heatcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{connection} = [draw, -latex', ultra thick]
\tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
\tikzstyle{heat_flow} = [draw, -latex', ultra thick, color=heatcolor]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    \node [element] (inlet) {Inlet};
    \node [element, right=4em of inlet] (fan) {Fan};
    \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element, right=4em of splitter] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (corenozzle) {Core Nozzle};
    \node [element, below=4em of burner] (bypduct) {Bypass Duct};
    \node [element, below=4em of corenozzle] (bypnozzle) {Bypass Nozzle};

@@

@@

>>>>

\tikzstyle{element} = [rectangle, draw, fill=elementcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{shaft_element} = [rectangle, draw, fill=shaftcolor!20,
text width=10em, text centered, font=\LARGE, rounded corners, minimum height=4em]
\tikzstyle{heat_element} = [rectangle, draw, fill=heatcolor!20,
text width=9em, text centered, font=\LARGE, rounded corners, minimum height=6em]
\tikzstyle{connection} = [draw, -latex', ultra thick]
\tikzstyle{shaft} = [draw, line width=0.1cm, color=shaftcolor]
\tikzstyle{station_label} = [circle, draw, text width=2em, text centered, font=\LARGE]
\tikzstyle{line} = [draw]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    \node [element] (inlet) {Inlet};
    \node [element, right=4em of inlet] (fan) {Fan};
    \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element, right=4em of splitter] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (corenozzle) {Core Nozzle};
    \node [element, below=8em of burner] (bypduct) {Bypass Duct};
    \node [element, below=8em of corenozzle] (bypnozzle) {Bypass Nozzle};

@@

    % Create station labels
    % \node [station_label, below=8em of inlet.west] (1) {1};
    \node [station_label, below=6em of fan.west] (1) {1};
    % \node [station_label, below=8em of splitter.west] (13) {13};
    \node [station_label, below=6em of lpc.west] (2) {2};
    \node [station_label, below=6em of hpc.west] (25) {25};
    \node [station_label, below=6em of burner.west] (3) {3};
    \node [station_label, below=6em of hpt.west] (4) {4};
    \node [station_label, below=6em of lpt.west] (45) {45};
    \node [station_label, below=6em of corenozzle.west] (5) {5};
    \node [station_label, below=6em of bypnozzle.west] (17) {17};

@@

    % Draw station label connections
    % \path [line] (inlet.west) -- (1.north);
    \path [line] (fan.west) -- (1.north);
    % \path [line] (splitter.west) -- (13.north);
    \path [line] (lpc.west) -- (2.north);
    \path [line] (hpc.west) -- (25.north);
    \path [line] (burner.west) -- (3.north);
    \path [line] (hpt.west) -- (4.north);
    \path [line] (lpt.west) -- (45.north);
    \path [line] (corenozzle.west) -- (5.north);
    \path [line] (bypnozzle.west) -- (17.north);
